Next Generation Planning - Structuring and Sharing Environmental Drivers Data for the St. Lawrence System

### 2020-03-11 Revisions/Beauchesne-eDriversMS.Rmd
manuscript revisions to submit to Frontiers

The St. Lawrence is a vast and complex socio-ecological system providing a
wealth of services sustaining numerous economic sectors. These ecosystems are
subject to significant human pressures that overlap and potentially interact
with climate driven environmental changes. Our objective in this paper is to
systematically characterize the distribution and intensity of drivers in the
St. Lawrence System. To do so, we launch *eDrivers*, an open knowledge
platform gathering experts committed to structuring, standardizing and sharing
knowledge on drivers in support of science and management. We gathered data on
22 coastal, climate, fisheries and marine traffic drivers through
collaborations, existing environmental initiatives and open data portals. We
show that few areas of the St. Lawrence are free of cumulative exposure. The
Estuary, the Anticosti Gyre and coastal areas are particularly exposed,
especially in the vicinity of urban centers. We identified 6 areas of distinct
cumulative exposure regime that show that certain drivers typically co-occur
in different regions of the St. Lawrence and that coastal areas are exposed to
all driver types. Of particular concern are two threat complexes capturing
most exposure hotspots that show the convergence of contrasting exposure
regimes at the head of the Laurentian Channel. *eDrivers* was built on a
series of guiding principles upholding existing data management and open
science standards. We therefore expect it to evolve through time to address
knowledge gaps and refine current driver layers. Ultimately, we believe that
*eDrivers* represents a much needed solution that could radically influence
broad scale research and management practices by increasing knowledge accessibility
and interoperability.

@@

The St. Lawrence System, formed by one of the largest estuaries in the world,
the St. Lawrence Estuary, and a vast interior sea, the Gulf of St. Lawrence, is
a complex social-ecological system characterized by highly variable
environmental conditions and oceanographic processes
[@el-sabh1990a; @white1997; @dufour2007]. It constitutes a unique
and heterogeneous array of habitats suited for the establishment of diverse and
productive ecological communities [@savenkoff2000]. As a result, the St.
Lawrence System provides a wealth of ecosystem services that have historically
and contemporarily benefited the Canadian economy. It sustains a rich fisheries
industry targeting more than 50 species, serves as the gateway to eastern
North-America by granting access to more than 40 ports and the most densely
populated Canadian region, hosts a booming tourism industry and an expanding
aquaculture production, fosters emerging activities and boasts a yet untapped
hydrocarbon potential [@beauchesne2016; @schloss2017; @archambault2017]. With
major investments recently made and more forthcoming in economic and
infrastructure development and research [*e.g.* @governmentofquebec2015; @rqm2018], an intensification of the human footprint is likely in the St. Lawrence System.

As elsewhere in the world [see @halpern2015a], this intensifying human footprint
will likely result in increasingly intricate environmental exposure regimes,
*i.e.* suites of overlapping and potentially interacting environmental drivers
threatening ecosystems, habitats or ecological communities. Drivers, often
referred to as stressors or pressures, are any externalities that affect
environmental processes and disturb natural systems. Drivers may originate from
natural or human-induced biophysical processes (*e.g.* sea surface temperature
anomalies and hypoxia) or directly from anthropogenic activities (*e.g.*
fisheries and marine pollution). The potential for complex interactions between
drivers is the largest uncertainty when studying or predicting environmental
impacts [@darling2008; @cote2016]. Multiple drivers can combine
non-linearly and result in effects that are greater (synergistic effect) or
lower (antagonistic effect) than the sum of individual effects
[@crain2008; @darling2008; @cote2016].

The uncertainty associated with complex driver interactions must therefore be taken into account when investigating environmental impacts [@cote2016], yet most research on driver effects in marine environments remains overwhelmingly focused on single driver assessments [@obrien2019]. Increasing exposure and the experiences of past ecological tragedies such as the collapse of cod fisheries [@frank2005; @dempsey2018] and the decline of the beluga and right whale populations [@plourde2014] together urge the need to characterize the distribution, intensity and overlap between drivers in the St. Lawrence System. This will provide critical information on areas most exposed to \textcolor{red}{\sout{cumulative}} drivers \textcolor{red}{\sout{and on the interaction potential of drivers}} in the St. Lawrence. It is also a necessary step towards the holistic and integrated management of the St. Lawrence System.

\textcolor{blue}{Gathering knowledge is a major component of any holistic approach, which typically involve the selection and description of valued ecosystem component (\textit{e.g.} habitats or species) and driver indicators, the assessment of the exposure and vulnerability of valued components to drivers, the selection of a proper spatio-temporal scale, site monitoring, and public and stakeholder participation (Dubé and Munkittrick 2001).} <!-- [@dube2001] jones2016 ???? Noble2013??? -->
Gathering environmental \textcolor{red}{\sout{data}} \textcolor{blue}{knowledge} for large scale, \textcolor{red}{\sout{systematic}} \textcolor{blue}{holistic} initiatives can, however, be a very challenging and time consuming – not to say painful – process. On one hand, there is an overwhelming and expanding wealth of data available. Such information overload may inhibit our ability to make decisions based on scientific information, promote massive effort duplication, disproportionately appropriate research funds to certain sectors, and obscure knowledge gaps amid a sea of information [@eppler2004]. On the other hand, crucial data are lacking and remain largely unavailable or inaccessible for a variety of reasons, including proprietary rights, lack of organizational time, capacity and training, and in some rare cases unwillingness to share, curtailing our ability for appropriate decision-making.

There are now initiatives that address this issue by assembling, organizing and
sharing environmental knowledge, such as the Ocean Biogeographic Information
System [OBIS; @obis2019] for biotic data and Bio-ORACLE [@tyberghein2012] for
abiotic data.
However, equivalent platforms for environmental drivers have largely focused on
single drivers (e.g. Global Fishing Watch) and platforms collating
data and knowledge on multiple drivers in a comparable and interoperable way
remain conspicuously missing [but see @halpern2015]. This is in spite of
integrated management and assessment approaches needing efficient data reporting,
standardized data management practices and tools tailored to the study of the
effects of multiple drivers [@dafforn2016; @stock2018]. An additional objective
thus emerged in the process of addressing our initial goals: sharing the
knowledge gathered through the description of drivers in the St.
Lawrence.

Our main objective in this study is to characterize the distribution and
intensity of drivers in the St. Lawrence. More specifically, we aim to: 1)
identify areas of high cumulative exposure\textcolor{red}{\sout{, 2) identify drivers that are likely to interact in the St. Lawrence}} and \textcolor{red}{\sout{3)}} \textcolor{blue}{2)} characterize areas with similar cumulative exposure regimes.
\textcolor{red}{\sout{Here we focus solely on drivers, one of four elements required to evaluate environmental impacts, *i.e.* drivers, ecosystem components of interest (*e.g.* habitats or species) and the exposure and the vulnerability of the ecosystem components to drivers.}}
\textcolor{blue}{Here we focus solely on drivers, aiming at better understanding their distribution in the St. Lawrence and at facilitating the widespread availability of their characterization for holistic assessments and management approaches.}
We achieve these objectives with the development of an
open knowledge platform named *eDrivers*. The platform was designed to
facilitate collaboration, real-time assessments of cumulative exposure and to
evolve with the addition of information and threats to the St-Lawrence ecosystems.

@@

The St. Lawrence drains over 25% of global freshwater reserves through its
connexion to the Great Lakes Basin. The Basin is home to over 45 million
North-Americans, *i.e.* 15 and 30 million in Canada and the United States,
respectively [@archambault2017]. The St. Lawrence itself boasts a much lower
population of approximately 1 million Canadians living within 10 km of the
coast, with populations mainly located in a few coastal cities in the Estuary
and the Southern Gulf [@statistics-canada2017].

@@

The list of drivers for which we sought data was informed by a global
cumulative impact assessment initiative [@halpern2008a; @halpern2015a],
regional holistic evaluations of the state of the St. Lawrence [@dufour2007;
@benoit2012], and communications with regional experts. We integrated datasets
from regional experts and also use global data from the global cumulative
impact assessment initiative [@halpern2008a; @halpern2015a] available from the
National Center for Ecological Analysis and Synthesis (NCEAS) online data
repository [Table 1; @halpern2015]. We selected global data that were
unavailable at the regional scale and that were available at a resolution
adequate for use at the scale of the St. Lawrence (*e.g.* marine pollution).

@@

Drivers with non-normal frequency distributions were log-transformed (Figure S1)
and all drivers were scaled between 0 and 1 to allow driver comparisons. The
99th quantile of individual driver distribution was used as the upper bound for
scaling to control for extreme values and produce maps of individual drivers
(Figure S2). All drivers were embedded in a regular grid composed of 245604
$1 km^2$ hexagonal cells to construct the integrated dataset used for the
analyses.

@@

\textcolor{red}{\sout{Interactions among drivers were investigated using the cumulative footprint ($F$) between pairs of drivers (objective 2). The intensity at which pairs of drivers co-occur was evaluated using a two-dimensional kernel density estimate. As there are 231 pairwise combinations between 22 drivers, we focus on a single example using hypoxia and demersal destructive fisheries, two drivers known to occur mainly in deeper areas of the St. Lawrence and, hence, an interaction between the effects of the two drivers could be anticipated.}}
\textcolor{blue}{As an introduction to indicators of cumulative exposure (objective 1), we begin by presenting a simplifed 2-driver example focusing on hypoxia and demersal destructive fisheries, two drivers known to occur mainly in deeper areas of the St. Lawrence. Driver co-ccurrence was evaluated spatially by summing the scaled intensity of drivers in each grid cell. The intensity at which pairs of drivers co-occur was evaluated using a two-dimensional kernel density estimate to investigate the relative intensity at which these two drivers typically co-occur.}

@@

In order to \textcolor{red}{\sout{better capture potential interactions between drivers (objective 2) and to}}identify areas with similar exposure regimes (objective 3), we identify threat complexes using a clustering approach [*e.g.* see @bowler2019]. We use the term clusters in presenting the methods, but use threat complex when discussing the results on cumulative exposure regimes.

@@

\textcolor{blue}{The individual or interactive effect of both drivers is thus species- and community-dependent and the co-occurrence of drivers in itself is not an evidence of driver interaction. Assuming that driver co-occurrence is a prerequisite for driver interactions, however, it is reasonable to expect interactions to occur in areas where both drivers co-occur at high relative intensities. }

@@

\textcolor{red}{\sout{While the focus of our paper has been on the description of drivers in the St. Lawrence, drivers are but one of the 4 elements required to properly evaluate environmental impacts. This single knowledge node should be weaved with other, comparable, nodes required for integrated management approaches such as species distribution and marine protected areas. Ultimately, all of these knowledge nodes could be weaved together through social-ecological metanetworks (Dee et al. 2017).}}
\textcolor{blue}{A caveat to our initiative is that it focuses on a single element required for fully operational impact assessments. Data that provide knowledge on the exposure of ecosystems to drivers are called stressor-based indicators (Dube and Munkittrick 2001; Dubé 2003; Jones 2016). These indicators efficently identify potential local impacts and can be proactively linked to decision-making, yet assume complete knowledge of drivers and fail to diagnose impacts on valued components or non-additive effects (Dube and Munkittrick 2001; Dubé 2003). In contrast, effect-based indicators are direct measurements of valued components (\textit{e.g.} species abundance and biodiversity) and inherently capture the effects of multiple drivers (Dube and Munkittrick 2001; Dubé 2003). While effect-based indicators are considered superior to stressor-based indicators, they fail to ascribe observed effects to specific drivers (Dube and Munkittrick 2001; Dubé 2003). Stressor-based and effect-based indicators are therefore both required to diagnose causes of ecosystem change (Dube 2003; Jones 2016). As a knowledge node on stressor-based indicators, \textit{eDrivers} should be weaved with other, comparable, nodes describing valued ecosystem components that can be linked to drivers and allow a better understanding of cumulative impacts. Ultimately, multiple knowledge nodes could be weaved together through social-ecological metanetworks analyses (Dee et al. 2016).}

>>>>

The St. Lawrence is a vast and complex socio-ecological system providing a
wealth of services sustaining numerous economic sectors. These ecosystems are
subject to significant human pressures that overlap and potentially interact
with climate driven environmental changes. Our objective in this paper is to
systematically characterize the distribution and intensity of drivers \textcolor{blue}{of change} in the
St. Lawrence System. To do so, we launch *eDrivers*, an open knowledge
platform gathering experts committed to structuring, standardizing and sharing
knowledge on drivers \textcolor{blue}{of change} in support of science and management. We gathered data on
22 coastal, climate, fisheries and marine traffic drivers through
collaborations, existing environmental initiatives and open data portals. We
show that few areas of the St. Lawrence are free of cumulative exposure. The
Estuary, the Anticosti Gyre and coastal areas are particularly exposed,
especially in the vicinity of urban centers. We identified 6 areas of distinct
cumulative exposure regime that show that certain drivers \textcolor{blue}{of change} typically co-occur
in different regions of the St. Lawrence and that coastal areas are exposed to
all driver types. Of particular concern are two threat complexes capturing
most exposure hotspots that show the convergence of contrasting exposure
regimes at the head of the Laurentian Channel. *eDrivers* was built on a
series of guiding principles upholding existing data management and open
science standards. We therefore expect it to evolve through time to address
knowledge gaps and refine current driver layers. Ultimately, we believe that
*eDrivers* represents a much needed solution that could radically influence
broad scale research and management practices by increasing knowledge accessibility
and interoperability.

@@

The St. Lawrence System, formed by one of the largest estuaries in the world\textcolor{red}{\sout{, the St. Lawrence Estuary,}}
and a vast interior sea\textcolor{red}{\sout{, the Gulf of St. Lawrence}}, is
a complex social-ecological system characterized by highly variable
environmental conditions and oceanographic processes
[@el-sabh1990a; @white1997; @dufour2007]. It constitutes a unique
and heterogeneous array of habitats suited for the establishment of diverse and
productive ecological communities [@savenkoff2000]. As a result, the St.
Lawrence System provides a wealth of ecosystem services that have \textcolor{red}{\sout{historically and contemporarily}}
benefited the Canadian economy. It sustains a rich fisheries
industry targeting more than 50 species, serves as the gateway to eastern
North-America by granting access to more than 40 ports and the most densely
populated Canadian region, hosts a booming tourism industry and an expanding
aquaculture production, fosters emerging activities and boasts a yet untapped
hydrocarbon potential [@beauchesne2016; @schloss2017; @archambault2017]. With
major investments recently made and more forthcoming in economic and
infrastructure development and research [*e.g.* @governmentofquebec2015; @rqm2018], an intensification of the human footprint is likely in the St. Lawrence System.

As elsewhere in the world [see @halpern2015a], this intensifying human footprint
will likely result in increasingly intricate environmental exposure regimes,
*i.e.* suites of overlapping \textcolor{red}{\sout{and potentially interacting}} environmental drivers \textcolor{blue}{of change}
threatening ecosystems, habitats or ecological communities. Drivers \textcolor{blue}{of change}, often referred to as stressors or pressures \textcolor{blue}{and hereafter called drivers for simplicity}, are any externalities that affect
environmental processes and disturb natural systems. Drivers may originate from
natural or human-induced biophysical processes (*e.g.* sea surface\textcolor{blue}{-water} temperature
anomalies and hypoxia) or directly from anthropogenic activities (*e.g.*
fisheries and marine pollution). The potential for complex interactions between
\textcolor{blue}{co-occurring} drivers is the largest uncertainty when studying or predicting environmental impacts [@darling2008; @cote2016]. Multiple drivers can combine non-linearly and result in effects that are greater (synergistic effect) or lower (antagonistic effect) than the sum of individual effects
[@crain2008; @darling2008; @cote2016].

The uncertainty associated with complex driver interactions must therefore be taken into account when investigating environmental impacts [@cote2016], yet most research on driver effects in marine environments remains overwhelmingly focused on single driver assessments [@obrien2019]. Increasing exposure and the experiences of past ecological tragedies such as the collapse of cod fisheries [@frank2005; @dempsey2018] and the decline of the beluga and right whale populations [@plourde2014] together urge the need to characterize the distribution, intensity and \textcolor{red}{\sout{overlap}} \textcolor{blue}{co-occurrence} between drivers in the St. Lawrence System. \textcolor{blue}{The impacts of drivers, whether individually or in combination, depend on species-specific vulnerabilities. Driver co-occurrence alone is therefore not sufficient evidence to claim interactions among drivers. However, as drivers must co-occur to interact, the likelihood of interactions will increase with the number of drivers co-occurring.} \textcolor{red}{\sout{This will}} \textcolor{blue}{Describing drivers will therefore} provide critical information on areas most exposed to \textcolor{red}{\sout{cumulative}} drivers \textcolor{red}{\sout{and on the interaction potential of drivers}} in the St. Lawrence. It is also a necessary step towards the holistic and integrated management of the St. Lawrence System.

\textcolor{blue}{Holistic approaches typically involve, but are not limited to, the following steps: selecting and describing valued ecosystem components (\textit{e.g.} habitats and species) and drivers (\textit{e.g.} marine traffic and ocean acidification), assessing the exposure and vulnerability of valued components to drivers, selecting a proper spatio-temporal scale, monitoring, and public and stakeholder participation (Dubé and Munkittrick 2001).} <!-- [@dube2001] jones2016 ???? Noble2013??? -->
Gathering environmental
\textcolor{red}{\sout{data for large scale, systematic}}
\textcolor{blue}{knowledge for holistic}
initiatives can, however, be a very challenging and time consuming – not to say painful – process. On one hand, there is an overwhelming and expanding wealth of data available. Such information overload may inhibit our ability to make decisions based on scientific information, promote massive effort duplication, disproportionately appropriate research funds to certain sectors, and obscure knowledge gaps amid a sea of information [@eppler2004]. On the other hand, crucial data are lacking and remain largely unavailable or inaccessible for a variety of reasons, including proprietary rights, lack of organizational time, capacity and training, and in some \textcolor{red}{\sout{rare}} cases unwillingness to share, curtailing our ability for appropriate decision-making.

There are now initiatives that \textcolor{blue}{facilitate the data gathering process} \textcolor{red}{\sout{address this issue}} by assembling, organizing and sharing environmental knowledge, such as the Ocean Biogeographic Information
System [OBIS; @obis2019] for biotic data and Bio-ORACLE [@tyberghein2012] for
abiotic data.
However, equivalent platforms for environmental drivers have largely focused on
single drivers (e.g. Global Fishing Watch) and platforms collating
data and knowledge on multiple drivers in a comparable and interoperable way
remain conspicuously missing [but see @halpern2015]. This is in spite of
integrated management and assessment approaches needing efficient data reporting,
standardized data management practices and tools tailored to the study of the
effects of multiple drivers [@dafforn2016; @stock2018]. An additional objective
thus emerged in the process of addressing our initial goals: \textcolor{red}{\sout{sharing the knowledge gathered through the description of drivers in the St. Lawrence.}} \textcolor{blue}{sharing information about the distribution and intensity of drivers of change in the St.Lawrence.}

Our main objective in this study is to characterize the distribution and
intensity of drivers in the St. Lawrence. More specifically, we aim to: 1)
identify areas of high cumulative exposure\textcolor{red}{\sout{, 2) identify drivers that are likely to interact in the St. Lawrence}} and \textcolor{red}{\sout{3)}} \textcolor{blue}{2)} characterize areas with similar cumulative exposure regimes.
\textcolor{red}{\sout{Here we focus solely on drivers, one of four elements required to evaluate environmental impacts, *i.e.* drivers, ecosystem components of interest (*e.g.* habitats or species) and the exposure and the vulnerability of the ecosystem components to drivers.}}
\textcolor{blue}{Here, we focus solely on drivers, aiming at better understanding their distribution in the St. Lawrence and at facilitating the widespread availability of their characterization for holistic assessments and management approaches.}
We achieve these objectives with the development of an
open knowledge platform named *eDrivers*. The platform was designed to
facilitate collaboration, real-time assessments of cumulative exposure and to
evolve with the addition of information and threats to the St-Lawrence ecosystems.

@@

The St. Lawrence drains over 25% of global freshwater reserves through its
connexion to the Great Lakes Basin\textcolor{red}{\sout{. The Basin}}\textcolor{blue}{, which }is home to over 45 million
North-Americans, *i.e.* 15 and 30 million in Canada and the United States,
respectively. The St. Lawrence itself boasts a much lower
population of approximately 1 million Canadians living within 10 km of the
coast, with populations mainly located in a few coastal cities in the Estuary
and the Southern Gulf [@statistics-canada2017].

@@

\textcolor{red}{\sout{The list of drivers for which we sought data was informed by}} \textcolor{blue}{Drivers selection was informed by} a global
cumulative impact assessment initiative [@halpern2008a; @halpern2015a] \textcolor{blue}{and available from the National Center for Ecological Analysis and Synthesis (NCEAS) online data repository (Halpern et al. 2015)},
regional holistic evaluations of the state of the St. Lawrence [@dufour2007;
@benoit2012], and communications with regional experts (Table 1).
\textcolor{red}{\sout{We integrated datasets from regional experts and also use global data from the global cumulative impact assessment initiative [@halpern2008a; @halpern2015a]  available from the National Center for Ecological Analysis and Synthesis (NCEAS) online data repository [Table 1; @halpern2015].}} We selected global data that were
unavailable at the regional scale and that were available at a resolution
adequate for use at the scale of the St. Lawrence (*e.g.* marine pollution).

@@

Drivers with non-normal frequency distributions were log-transformed,
\textcolor{blue}{as in Halpern et al. 2008, to minimize the impact of extreme outliers that may or may not be real observations} (Figure S1)\textcolor{blue}{,} and all drivers were scaled between 0 and 1 to allow driver comparisons. The 99th quantile of individual driver distribution was used as the upper bound for scaling \textcolor{red}{\sout{to control for extreme values and produce maps of individual drivers (Figure S2)}}. All drivers were embedded in a regular grid composed of 245604 $1 km^2$ hexagonal cells to construct the integrated dataset used for the
analyses \textcolor{blue}{(Figure S2)}.

@@

\textcolor{red}{\sout{Interactions among drivers were investigated using the cumulative footprint ($F$) between pairs of drivers (objective 2). The intensity at which pairs of drivers co-occur was evaluated using a two-dimensional kernel density estimate. As there are 231 pairwise combinations between 22 drivers, we focus on a single example using hypoxia and demersal destructive fisheries, two drivers known to occur mainly in deeper areas of the St. Lawrence and, hence, an interaction between the effects of the two drivers could be anticipated.}}
\textcolor{blue}{As an introduction to indicators of cumulative exposure (objective 1), we begin by presenting a simplifed 2-driver example focusing on hypoxia and demersal destructive fisheries, two drivers known to occur mainly in deeper waters of the St. Lawrence. Driver co-ccurrence was evaluated spatially by summing the scaled intensity of drivers in each grid cell. The intensity at which pairs of drivers co-occur was evaluated using a two-dimensional kernel density.}

@@

In order to \textcolor{red}{\sout{better capture potential interactions between drivers (objective 2) and to}}identify areas with similar exposure regimes (objective \textcolor{red}{\sout{3}}\textcolor{blue}{2}), we identify threat complexes using a clustering approach [*e.g.* see @bowler2019]. We use the term clusters in presenting the methods, but use threat complex when discussing the results on cumulative exposure regimes.

@@

@@

\textcolor{red}{\sout{While the focus of our paper has been on the description of drivers in the St. Lawrence, drivers are but one of the 4 elements required to properly evaluate environmental impacts. This knowledge node should be weaved with other, comparable, nodes required for integrated management approaches such as species distribution and marine protected areas. Ultimately, all of these knowledges could be weaved together through social-ecological metanetworks (Dee et al. 2017).}}
\textcolor{blue}{The next step will be the inclusion of other types of knowledge to our initiative. Our focus has been on a single element required for fully operational impact assessments. Data that provide knowledge on the exposure of ecosystems to drivers are called stressor-based indicators (Dube and Munkittrick 2001; Dubé 2003; Jones 2016). These indicators efficently identify potential local impacts and can be proactively linked to decision-making, yet assume complete knowledge of drivers but fail to diagnose impacts on valued components or non-additive effects (Dube and Munkittrick 2001; Dubé 2003). In contrast, effect-based indicators are direct measurements of valued components (\textit{e.g.} species abundance and biodiversity) and inherently capture the effects of multiple drivers (Dube and Munkittrick 2001; Dubé 2003). Whereas effect-based indicators are considered superior to stressor-based indicators, they fail to ascribe observed effects to specific drivers (Dube and Munkittrick 2001; Dubé 2003). Stressor-based and effect-based indicators are, therefore, both required to diagnose causes of ecosystem change (Dube 2003; Jones 2016). As a collection of knowledge on stressor-based indicators, \textit{eDrivers} should be weaved with other, comparable, collections of knowledge describing valued ecosystem components that can be linked to drivers and allow for a better understanding of cumulative impacts. Ultimately, interdisciplinary colections of knowledge could be weaved together through social-ecological metanetworks analyses (Dee et al. 2016).}
